\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amssymb,amsthm}

\newtheorem*{theorem}{Theorem}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}

% List styles
\renewcommand{\theenumii}{\roman{enumii}}
\renewcommand{\labelenumii}{(\theenumii)}

\begin{document}
    \begin{center}
        \Large \bf MATH1081 Test 2 past solutions
    \end{center}

    \begin{center}
        \large \bf \copyright UNSW MATHSOC 2012
    \end{center}

    \vspace{10mm}

    These solutions were written by Johann Blanco and typed up by Evgeny
    Martynov. Please be ethical with this resource. It is for the use of
    MATHSOC members, so {\bf do not repost it on other forums or groups
    without asking for permission}. If you appreciate this resource,
    please consider supporting us by coming to our events and buying our
    T-shirts! Also, happy studying :)

    We cannot guarantee that our working is correct, or that it would
    obtain full marks - please notify us of any errors or typos at
    unswmathsoc@gmail.com, or on our Facebook page. There are sometimes
    multiple methods of solving the same question. Remember that in the
    real class test, you will be expected to explain your steps and
    working out.

    This document was written in mathematical typesetting language
    called \LaTeX(pronounced lay-teck). You can learnt a lot about how
    \LaTeX works by downloading the code for existing documents and
    fiddling around with it. If you would like to try this, send an
    email to unswmathsoc@gmail.com and  we can send you the code for
    this file.

    \newpage
    \input{3-2008-3a}
    \newpage
    \input{3-2008-1a}
    \newpage
    \input{3-2009-2a}
    \newpage
    \input{3-2009-1a}
\end{document}
